Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-09 msbr_reproc.tex
minor grammar fix

The current paper presents the single-cell model developed using the
continuous-energy Serpent 2 Monte Carlo reactor physics software. It was 
employed to find an equilibrium core composition and core depletion of the 
single-cell unit. 
All calculations presented in this paper were performed using the Serpent 2 
code version 2.1.29 with ENDF/B-VII.0
nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}. Serpent 
2 is an improvement upon Serpent 1, and contains a complete 
redesign of memory management using hybrid OpenMP + MPI parallelization.  This 
hybrid parallelization is important in depletion calculations using computer 
clusters with multiple cores \cite{leppanen_serpent_2015}. This work used the 
built-in Serpent 2 depletion capabilities and its built-in online reprocessing 
subroutine. Another feature of the \gls{MSBR}, its circulating liquid fuel and 
corresponding delayed neutron precursor drift, is not treated here.

>>>>

The current paper presents a single-cell model developed using the
continuous-energy Serpent 2 Monte Carlo reactor physics software. It was 
employed to establish a Serpent-based method for finding the equilibrium core composition and 
core depletion of the \gls{MSBR}.
All calculations presented in this paper were performed using the Serpent 2 
code version 2.1.29 with ENDF/B-VII.0
nuclear data \cite{leppanen_serpent_2012,chadwick_endf/b-vii.0:_2006}. Serpent 
2 is an improvement upon Serpent 1, and contains a complete 
redesign of memory management using hybrid OpenMP + MPI parallelization.  This 
hybrid parallelization is important in depletion calculations using computer 
clusters with multiple cores \cite{leppanen_serpent_2015}. This work used the 
built-in Serpent 2 depletion capabilities and its built-in online reprocessing 
subroutine. Another feature of the \gls{MSBR}, its circulating liquid fuel and 
corresponding delayed neutron precursor drift, is not treated here.
